An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative

### 2019-05-27 Tex/elsevier/trindade_appliedenergy_rev0.tex
new code optimization and paper

\documentclass[10pt,conference]{IEEEtran}
% \documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\bibliographystyle{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm,algorithmic}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{textcomp}
\usepackage{xcolor}
\def \BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

 \renewcommand{\baselinestretch}{0.965}

@@

\title{Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems}
%
%\author{\IEEEauthorblockN{Alessandro Trindade}
%\IEEEauthorblockA{
%\textit{Federal University of Amazonas}, Brazil \\
%alessandrotrindade@ufam.edu.br}
%\and
%\IEEEauthorblockN{Lucas Cordeiro}
%\IEEEauthorblockA{
%\textit{University of Manchester}, UK \\
%lucas.cordeiro@manchester.ac.uk }
%}
%
\maketitle

@@

\begin{IEEEkeywords}
automated verification, model checking, program synthesis, electrical systems, and solar photovoltaic systems.
\end{IEEEkeywords}

@@

\begin{equation}
\label{eq:Ecorrected}
\scriptstyle E_{corrected} = \dfrac{\scriptstyle E_{consumption}}{ \scriptstyle \eta_{b} \eta_{c} \eta_{i} }.
\end{equation}
We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
\begin{equation}
\label{eq:Ep}
\scriptstyle E_{p} = \scriptstyle Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
\end{equation}
\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
\begin{equation}
\label{eq:NTPmin}
\scriptstyle N_{TPmin} = \dfrac{\scriptstyle E_{corrected}}{\scriptstyle E_{p}}.
\end{equation}

@@

\begin{equation}
\label{eq:NPSmin}
\dfrac{\scriptstyle V_{mppt,min}}{\scriptstyle V_{maxPower,TempMax}} \scriptstyle \leq \scriptstyle N_{PSmin} \leq \dfrac{\scriptstyle V_{mppt,max}}{\scriptstyle V_{maxPower,TempMin}},
\end{equation}
\begin{equation}
\label{eq:NPPmin}
\scriptstyle N_{PPmin} = \dfrac{\scriptstyle P_{total}}{\scriptstyle Number\,Panels\,Series \scriptstyle \times \scriptstyle P_{max,ref}},
\end{equation}
\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
%, $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
\begin{equation}
\label{eq:Cbank}
\scriptstyle C_{bank} \scriptstyle = \dfrac{\scriptstyle E_{corrected} \scriptstyle \times \scriptstyle autonomy}{\scriptstyle V_{system} \scriptstyle \times \scriptstyle DOD},
\end{equation}
\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
Secondly, the total (minimum) number of batteries is computed as 
\begin{equation}
\label{eq:Nbtotal}
\scriptstyle N_{B}total = \scriptstyle N_{BS}min \scriptstyle \times \scriptstyle N_{BP}min = \dfrac{\scriptstyle V_{system}}{\scriptstyle V_{bat}} \scriptstyle \times \dfrac{\scriptstyle C_{bank}}{\scriptstyle 1 \,Battery \, Capacity}.
\end{equation}
Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem} to the charge controller voltage: 
\begin{equation}
\label{eq:vcvsystem}
\scriptstyle V_{c} = \scriptstyle V_{system}.
\end{equation}

@@

\begin{equation}
\label{eq:iscamb}
\scriptstyle I_{sc,amb} = \dfrac{\scriptstyle G}{\scriptstyle G_{ref}} \left[ \scriptstyle I_{sc,ref} + \scriptstyle \mu_{I} \scriptstyle \times \scriptstyle (T-25) \right]. 
\end{equation}

@@

\begin{equation}
\label{eq:icmin}
\scriptstyle I_{c,min} = \scriptstyle I_{sc,amb} \times \scriptstyle N_{PP},
\end{equation}
\begin{equation}
\label{eq:icicmin}
\scriptstyle I_{c} \geq \scriptstyle I_{c,min}.
\end{equation}
The inverter sizing check is performed by means of three equations. Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
\begin{equation}
\label{eq:vindc} 
\scriptstyle V_{in}DC = \scriptstyle V_{system}.
\end{equation}
\begin{equation}
\label{eq:voutac} 
\scriptstyle V_{out}AC = \scriptstyle V_{AC}.
\end{equation}
\begin{equation}
\label{eq:invcheck} 
\left[ (\scriptstyle Demand \leq \scriptstyle P_{AC,ref}) \, \scriptstyle and \, \scriptstyle (P_{surge} \leq MAX_{AC,ref}) \right].
\end{equation}

@@

 \begin{scriptsize}

@@

  \end{scriptsize}

@@

\textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
%
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{trindadeThesis_menor}{}
%\vspace{12pt}
\end{document}

>>>>

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
%\modulolinenumbers[5]
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm,algorithmic}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{textcomp}
\usepackage{xcolor}

\journal{Applied Energy}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{frontmatter}

%\title{Innovative techno-economic optimization of stand-alone solar photovoltaic systems using automated formal synthesis} 
\title{An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative}
%
%\title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
%
%% Group authors per affiliation:
\author[mymainaddress]{Alessandro Trindade\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{alessandrotrindade@ufam.edu.br}
%\ead[url]{www.elsevier.com}

\author[mysecondaryaddress]{Lucas Cordeiro}

\address[mymainaddress]{Federal University of Amazonas, Av. Rodrigo Octávio, 6200, Coroado I, 69077-000 Manaus-AM-Brazil}
\address[mysecondaryaddress]{University of Manchester, School of Computer Science, Kilburn Building, Manchester M13 9PL}

@@

\begin{keyword}
automated verification \sep model checking \sep program synthesis \sep electrical systems \sep solar photovoltaic systems
\end{keyword}

\end{frontmatter}

%\linenumbers

@@

\begin{equation}
\label{eq:Ecorrected}
E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \eta_{c} \eta_{i} }.
\end{equation}

%
We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
%

\begin{equation}
\label{eq:Ep}
E_{p} = Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
\end{equation}

\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
%
The total minimum number of needed solar panels ($N_{TPmin}$) is computed as

\begin{equation}
\label{eq:NTPmin}
N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
\end{equation}

@@

\begin{equation}
\label{eq:NPSmin}
\dfrac{V_{mppt,min}}{V_{maxPower,TempMax}} \leq N_{PSmin} \leq \dfrac{V_{mppt,max}}{V_{maxPower,TempMin}},
\end{equation}

\begin{equation}
\label{eq:NPPmin}
N_{PPmin} = \dfrac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}},
\end{equation}

\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
%, $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
%
Regarding batteries, we must first define the total capacity of the battery bank, which can be described as

\begin{equation}
\label{eq:Cbank}
C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD},
\end{equation}

\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
%
Secondly, the total (minimum) number of batteries is computed as

\begin{equation}
\label{eq:Nbtotal}
N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{1 \,Battery \, Capacity}.
\end{equation}

Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem} to the charge controller voltage: 
\begin{equation}
\label{eq:vcvsystem}
V_{c} = V_{system}.
\end{equation}

@@

\begin{equation}
\label{eq:iscamb}
I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
\end{equation}

@@

\begin{equation}
\label{eq:icmin}
I_{c,min} = I_{sc,amb} \times N_{PP},
\end{equation}

\begin{equation}
\label{eq:icicmin}
I_{c} \geq I_{c,min}.
\end{equation}

The inverter sizing check is performed by means of three equations. Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
%
\begin{equation}
\label{eq:vindc} 
V_{in}DC = V_{system}.
\end{equation}

\begin{equation}
\label{eq:voutac} 
V_{out}AC = V_{AC}.
\end{equation}

\begin{equation}
\label{eq:invcheck} 
\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
\end{equation}

@@

@@

@@

\textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
%
% argument is your BibTeX string definitions and bibliography database(s)
\section*{References}
\bibliography{trindadeThesis}{}
%\vspace{12pt}
\end{document}
